\begin{thebibliography}{99}
%MCE-introduction%
\bibitem{Gschneidner-RPP-2005}
	K. A. Gschneidner, Jr., V. K. Pecharsky, A. O. Tsokol,
	Recent developments in magnetocaloric materials,
	Rep. Prog. Phys. 68 (2005) 1479-1539.

\bibitem{Kitanovski-Springer-2015}
	A. Kitanovski, J. Tus$\check{\rm e}$k, U. Tomc, U. Plaznik,
	M. O$\check{\rm z}$bolt, A. Poredo$\check{\rm s}$,
	Magnetocaloric Energy Conversion,
	Springer International Publishing 2016.

\bibitem{Numazawa-Cryog-2014}
	T. Numazawa, K. Kamiya, T. Utaki, K. Matsumoto,
	Magnetic refrigerator for hydrogen liquefaction,
	Cryogenics 62 (2014) 185.

\bibitem{Zhang-PhysB-2019}
	H. Zhang, R. Gimaev, B. Kovalev, K. Kamilov, V. Zverev, A. Tishin,
	Review on the materials and devices for magnetic refrigeration
	in the temperature range of nitrogen and hydrogen liquefaction,
	Physica B: Condens. Matter 558 (2019) 65-73.

\bibitem{Tishin-JMMM-2007}
	A. M. Tishin,
	Magnetocaloric effect: Current situation and future trends,
	J. Magn. Magn. Mater. 316 (2007) 351-357.

\bibitem{Smith-AEM-2012}
	A. Smith, C. R. H. Bahl, R. Bj{\o}rk, K. Engelbrecht, K. K. Nielsen, N. Pryds,
	Materials challenges for high performance magnetocaloric refrigeration Devices,
	Adv. Energy Mater. 2 (2012) 1288-1318.

\bibitem{Lyubina-JPD-2017}
	J. Lyubina,
	Magnetocaloric materials for energy efficient cooling,
	J. Phys. D: Appl. Phys. 50 (2017) 053002.

\bibitem{Gottschall-AEM-2019}
	T. Gottschall, K. P. Skokov, M. Fries, A. Taubel, I. Radulov, R. Scheibel,
	D. Benke, S. Riegg, O. Gutfleisch,
	Making a cool choice: The materials library of magnetic refrigeration,
	Adv. Energy Mater. 9 (2019) 1901322.


%ErCo2%
\bibitem{Wada-JAC-2001}
	H. Wada, Y. Tanabe, M. Shiga, H. Sugawara, H. Sato,
	Magnetocaloric effects of Laves phase Er(Co$_{1-x}$Ni$_{x}$)$_{2}$ compounds,
	J. Alloys Compd. 316 (2001) 245-249.

\bibitem{Oesterreicher-JAP-1970}
	H. Oesterreicher, L. M. Corliss, J. M. Hastings,
	Neutron diffraction study of the pseudobinary system ErCo$_{2}$-ErAl$_{2}$,
	J. Appl. Phys. 41 (1970) 2326.

\bibitem{Duc-JPFMP-1988}
	N. H. Duc, T. D. Hien, P. E. Brommer, J. M. Franse,
	Electronic and magnetic properties of Er$_{x}$Y$_{1-x}$Co$_{2}$ compounds,
	J. Phys. F: Met. Phys. 18 (1988) 275-294.

\bibitem{Gratz-JMMM-1994}
	E. Gratz, A. Lindbaum,
	The influence of the magnetic state on the thermal expansion
	in 1:2 rare earth intermetallic compounds,
	J. Magn. Magn. Mater. 137 (1994) 115-121.

\bibitem{Duc-Handbook-1999}
	N. H. Duc, T. Goto,
	Itinerant electron metamagnetism of Co sublattice
	in the lanthanide-cobalt intermetallics,
	K. A. Gschneidner Jr., L. Eyring (eds.),
	Handbook on Physics and Chemistry of Rare Earths,
	vol. 26, Elseveier, Amsterdam (1999),
	pp. 177-264.

\bibitem{Kozlenko-SciRep-2015}
	D. P. Kozlenko, E. Burzo, P. Vlaic, S. E. Kichanov, A. V. Rutkauskas, B. N. Savenko,
	Sequential cobalt magnetization collapse in ErCo$_{2}$:
	Beyond the limits of itinerant electron metamagnetism,
	Sci. Rep. 5 (2015) 8620.

\bibitem{Moon-JAP-1965}
	R. M. Moon, W. C. Koehler, J. Farrell,
	Magnetic structure of rare-earth-cobalt (RCo$_{2}$) intermetallic compounds,
	J. Appl. Phys. 36 (1965) 978.


%ErCo2-Substitution%
\bibitem{Duc-PhysC-1988}
	N. H. Duc, T. D. Hien, P. E. Brommer, and J. J. M. Franse,
	Magnetic properties of the Er(Co$_{1-x}$Cu$_{x}$)$_{2}$
	and Y(Co$_{1-x}$Cu$_{x}$)$_{2}$ compounds,
	Physica B Condens. Matter 149 (1988) 352-360.

\bibitem{Soares-JMMM-1999}
	M. R. Soares, A. Y. Takeuchi, F. Garcia, S. F. da Cunha, M. El Massalami,
	Magnetic phase diagram of the intermetallic series Er(Co$_{1-x}$Ni$_{x}$)$_{2}$,
	J. Magn. Magn. Mater. 202 (1999) 473-479.

\bibitem{Danis-JAC-2002}
	S. Dani$\check{\rm s}$, P. Javorsk$\acute{\rm y}$,
	D. Rafaja, V. Sechovsk$\acute{\rm y}$,
	Low-temperature transport and crystallographic studies of
	Er(Co$_{1-x}$Si$_{x}$)$_{2}$ and Er(Co$_{1-x}$Ge$_{x}$)$_{2}$,
	J. Alloys Compd. 345 (2002) 54-58.

\bibitem{Prokleska-JAC-2004}
	J. Prokle$\check{\rm s}$ka, J. Vejpravov$\acute{\rm a}$,
	D. Vasylyev, V. Sechovsk$\acute{\rm y}$,
	Magnetism of Er(Co$_{1-x}$X$_{x}$)$_{2}$ compounds:
	effects on structure and electronic properties,
	J. Alloys Compd. 383 (2004) 122-125.

\bibitem{Liu-JAP-2008}
	X. B. Liu, Z. Altounian,
	Magnetocaloric effect in Co-rich Er(Co$_{1-x}$Fe$_{x}$)$_{2}$ Laves phase,
	J. Appl. Phys. 103 (2008) 07B304.

\bibitem{Tang-NatCom-2022}
	X. Tang, H. Sepehri-Amin, N. Terada, A. Martin-Cid, I. Kurniawan, S. Kobayashi,
	H. Takeya, J. Lai, Y. Matsushita, T. Ohkubo, Y. Miura, T. Nakamura, K. Hono,
	Magnetic refrigeration material operating at a full temperature range
	required for hydrogen liquefaction,
	Nat. Commun. 13 (2022) 1817.
	

%ErCo2-Pressure experiments%
\bibitem{Kagayama-JMSJ-1999}
	T. Kagayama, G. Oomi, K. Fukamichi,
	Effect of pressure on the spontaneous magnetostriction of ErCo$_{2}$,
	J. Magn. Soc. Jpn. 23 (1999) 448-449.

\bibitem{Hauser-PRB-2000}
	R. Hauer, E. Bauer, E. Gratz, H. Muller, M. Rotter, H. Michor, G. Hilscher,
	A. S. Markosyan, K. Kamishima, T. Goto,
	Decoupling of the magnetic ordering of the rare-earth and the Co sublattice
	in Er$_{1-x}$Y$_{x}$Co$_{2}$ compounds driven by substitution or pressure,
	Phys. Rev. B 61 (2000) 1198.

\bibitem{Syshchenko-PRB-2001}
	O. Syshchenko, T. Fujita,V. Sechovsk$\acute{y}$, M. Divi$\check{\rm s}$, H. Fujii,
	Magnetism in ErCo$_{2}$ under high pressure,
	Phys. Rev. B 63 (2001) 054433.

\bibitem{Ishimatsu-PRB-2007}
	N. Ishimatsu, S. Miyamoto, H. Maruyama, J. Chaboy, M. A. Laguna-Marco, N. Kawamura,
	Experimental evidence of pressure-induced suppression of the cobalt magnetic moment in ErCo$_{2}$,
	Phys. Rev. B 75 (2007) 180402(R).


%Magnetocaloric particles & Our EIGA experiments%
\bibitem{Yu-IJR-2010}
	B. Yu, M. Liu, P. W. Egolf, A. Kitanovski,
	A review of magnetic refrigerator and heat pump prototypes,
	Int. J. Refrig. 33 (2010) 1029-1060.
	
\bibitem{Tusek-IJR-2013}
	J. Tu$\check{\rm s}$ek, A. Kitanovski, A. Poredo$\check{\rm s}$,
	Geometrical optimization of packed-bed and parallel-plate active magnetic regenerators,
	Int. J. Refrig. 36 (2013) 1456-1464.

\bibitem{TDY-HoB2-2021}
	T. D. Yamamoto, H. Takeya, A. T. saito, K. Terashima, P. B. Castro, T. Numazawa, Y. Takano,
	Gas-atomized particles of giant magnetocaloric compound HoB$_{2}$	for magnetic hydrogen liquefiers,
	Appl. Phys. A 127 (2021) 301.

\bibitem{TDY-HoAl2-2022}
	T. D. Yamamoto, H. Takeya, A. T. saito, K. Terashima, T. Numazawa, Y. Takano,
	Magnetocaloric particles of the Laves phase compound HoAl$_{2}$ prepared by
	electrode induction melting gas atomization,
	J. Magn. Magn. Mater. 547 (2022) 168906.

\bibitem{TDY-HoB2-x-2022}
	T. D. Yamamoto, H. Takeya, P. B. Castro, A. T. saito, K. Terashima, T. Numazawa, Y. Takano,
	Effect of non-stoichiometry on magnetocaloric properties of HoB2 gas-atomized particles,
	IEEE Trans. Magn. 58 (2022) 2501406.


%Experiment
\bibitem{Suzuki-Cryog-2010}
	H. Suzuki, A. Inaba, C. Meingast,
	Accurate heat capacity data at phase transitions from relaxation calorimetry,
	Cryogenics 50 (2010) 693-699.


%Results and discussion
\bibitem{Tang-PRB-1992}
	Y. J. Tang, X. W. Cao, J. C. Ho, H. C. Ku,
	Low-temperature calorimetric study of magnetic ordering in erbium oxide,
	Phys. Rev. B 46 (1992) 1213-1215.

\bibitem{Banerjee-PhysLett-1964}
	B. K. Banerjee,
	On a generalised approach to first and second order magnetic transitions,
	Phys. Lett. 12 (1964) 16-17.

\bibitem{Zou-JAC-2015}
	J.-D. Zou, M. Yan, J.-L. Yao,
	Manipulation of the magnetic properties in Er$_{1-x}$Co$_{2}$ compounds
	by atomic vacancies,
	J. Alloys Compd. 632 (2015) 30-36.

\bibitem{Liu-APL-2007}
	G. J. Liu J. R. Sun, J. Shen, B. Gao, H. W. Zhang, F. X. Hu, B. G. Shen,
	Determination of the entropy changes in the compounds with
	a first-order magnetic transition,
	Appl. Phys. Lett. 90 (2007) 032507.


\bibitem{Caron-JMMM-2009}
	L. Caron, Z. Ou, T. T. Nguyen, D. T. Cam  Thanh, O. Tegus, E. Br$\ddot{\rm u}$ck,
	On the determination of the magnetic entropy change
	in materials with first-order transitions,
	J. Magn. Magn. Mater. 321 (2009) 3559-3566.


\bibitem{Cui-APL-2010}
	W. Cui, W. Liu, Z. Zhang,
	The origin of large overestimation of the magnetic entropy changes
	calculated directly by Maxwell relation,
	Appl. Phys. Lett. 96 (2010) 222509.

\bibitem{Franco-JPD-2017}
	V. Franco, J. Y. Law, A. Conde, V. Brabander, D. Y. Karpenkov,
	I. Radulov, K. Skokov, O. Gutfleisch,
	Predicting the tricritical point composition of
	a series of LaFeSi magnetocaloric alloys via universal scaling,
	J. Phys. D: Appl. Phys. 50 (2017) 414004.

%MCE table
\bibitem{Zhang-Intermet-2015}
	Y. Zhang, G. Wilde, X. Li, Z. Ren, L. Li,
	Magnetism and magnetocaloric effect in the ternary equiatomic \textit{RE}FeAl
	(\textit{RE} $=$ Er and Ho) compounds,
	Intermetallics 65 (2015) 61-65.

\bibitem{Li-JAC-2011}
	L. Li, K. Nishimura, H. Igawa, D. Huo,
	Magnetic properties and magnetocaloric effect in GdCo$_{3}$B$_{2}$ compound,
	J. Alloys Compd. 509 (2011) 4198-4200.

\bibitem{Li-IEEETM-2014}
	L. Li, O. Niehaus, B. Gerke, R. P$\ddot{\rm o}$ttgen,
	Magnetism and magnetocaloric effect in EuAuZn,
	IEEE Trans. Magn. 50 (2014) 2503604.

\bibitem{Hashimoto-ACEM-1986}
	T. Hashimoto, K. Matsumoto, T. Kurihara, T. Numazawa, A. Tomokiyo,
	H. Yayama, T. Goto, S. Todo, M. Sahashi,
	Investigation on the possibility of the RAl$_{2}$ system as refirgerant
	in an ericsson type magnetic refrigerator,
	Adv. Cryog. Eng. Mater. 32 (1986) 279.

\bibitem{Yamamoto-JAC-2004}
	T. A. Yamamoto, T. Nakagawa, K. Sako, T. Arakawa, H. Nitani,
	Magnetocaloric effect of rare earth mono-nitrides TbN and HoN,
	J. Alloys Compd. 376 (2004) 17-22.

\bibitem{Zhang-JPD-2016}
	Y. Zhang, Y. Yang, X. Xu, L. Hou, Z. Ren, X. Li, G. Wilde,
	Large reversible magnetocaloric effect in RE$_{2}$Cu$_{2}$In (RE $=$ Er and Tm)
	and enhanced refrigerant capacity in its composite materials,
	J. Phys. D: Appl. Phys. 49 (2016) 145002.

\bibitem{Zhang-JAP-2018}
	Y. Zhang, D. Guo, S. Geng, X. Lu, G. Wilde,
	Structure, magnetic and cryogenic magneto-caloric properties in
	intermetallic gallium compounds \textit{RE}$_{2}$Co$_{2}$Ga
	(\textit{RE} $=$ Dy, Ho, Er, and Tm),
	J. Appl. Phys. 124 (2018) 043903.

\bibitem{Wang-APL-2011}
	J. L. Wang, S. J. Campbell, J. M. Cadogan, A. J. Studer, R. Zeng, S. X. Dou,
	Magnetocaloric effect in layered NdMn$_{2}$Ge$_{0.4}$Si$_{1.6}$,
	Appl. Phys. Lett. 98 (2011) 232509.

\bibitem{Yi-Intermet-2017}
	Y. Yi, L. Li, K. Su, Y. Qi, D. Huo,
	Large magnetocaloric effect in a wide temperature range induced by
	two successive magnetic phase transitions in Ho$_{2}$Cu$_{2}$Cd compound,
	Intermetallics 80 (2017) 22-25.
	
\bibitem{Xu-JJAP-2011}
	Y. Xu, M. Yamazaki, P. Villars,
	Inorganic materials database for exploring the nature of material,
	Jpn. J. Appl. Phys. 50 (2011) 11RH02.

\end{thebibliography}

