\vspace{+1ex}
\begin{center}
\Large \textbf{Appendices} 
\end{center}

\vspace{+1ex}

\section{Experimental Details}
\input{tables/data_statistic.tex}
\label{sec:app:a}
The statistics of all datasets used in this work are shown in Table \ref{tab:dataset}, please refer to their original papers for corresponding download links.



\input{figures/model.tex}
For the GEC model, we build it with the \texttt{Fairseq}\footnote{\url{https://github.com/facebookresearch/fairseq}} toolkit \cite{ott2019fairseq}. The backbone model is a Transformer with the ``base'' configuration. To encode syntactic information, 3 GCN blocks are stacked. Other hyper-parameters and training tricks are directly taken from \citet{zhang2022syngec}. The architecture of our syntax-enhanced GEC model is depicted in Figure \ref{fig:model}.



For GOPar, we adopt the \texttt{Supar}\footnote{\url{https://github.com/yzhangcs/parser}} toolkit and follow the default settings. We employ ELECTRA \cite{DBLP:conf/iclr/ClarkLLM20} as its encoder. 
The training data is automatically derived from the CLang8 GEC dataset via tree projection.

To fill the gap between the word-level parsing results and the subword-level Transformer inputs, we assign the head non-terminal node of the original word to all internal subwords, thus creating a subword-level tree, as shown in Figure \ref{fig:sub}. Then, we feed such subword-level trees into our syntax-enhanced GEC models.

\input{figures/sub-convert.tex}

\section{Case Study}

\input{figures/example.tex}
\label{sec:case}
\textcolor{black}{A case study is presented in Figure \ref{fig:example}. 
There is a verb tense error in the source sentence and we should substitute ``is'' with ``was'' to correct it. The correction evidence for this error is ``yesterday'', which drops a hint that the past tense should be used here.}

\textcolor{black}{The tailored constituency tree from this work (in the top) indicates that the erroneous word ``is'' and the correction evidence ``yesterday'' are in the same ``VP'' phrase, while ``is'' and the noise information ``tomorrow'' are not (ignore the whole sentence constituent ``S''). What is more, the inserted pseudo non-terminal node ``SUB'' directly points out that ``is'' is a substituted error.}

\textcolor{black}{The tailored dependency tree from \citet{zhang2022syngec} (in the bottom) shows that ``is'' and ``yesterday'' are siblings and have the same father node ``cancelled'', and ``yesterday'' is a time modifier (``tmod''). The label ``SUB'' of the incoming arc of ``is'' also supports that ``is'' should be substituted.}

\textcolor{black}{In short, both kinds of syntax provide helpful clues for GEC from different perspectives.}

