%%
%% This is file `sample-acmsmall-submission.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `acmsmall-submission')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-acmsmall-submission.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[acmsmall,nonacm,screen]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
%\setcopyright{acmcopyright}
\setcopyright{none}

%\copyrightyear{2021}
%\acmYear{2022}
%\acmDOI{arX}
\usepackage{wrapfig}
\usepackage{csquotes}

\settopmatter{printacmref=false}

%%
%% These commands are for a JOURNAL article.


%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}


\usepackage{amsthm}
\usepackage{subcaption} 
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{comment}
\usepackage{tablefootnote}




\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\providecommand*\definitionautorefname{Def.}
\let\vec\mathbf
\usepackage{xcolor}
\newcommand\myworries[1]{\textcolor{red}{#1}}
%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{User-Specific Bicluster-based Collaborative Filtering: Handling Preference Locality, Sparsity and Subjectivity}
%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\let\vec\mathbf

\author{Miguel G. Silva}
\affiliation{%
  \institution{LASIGE and Faculdade de Ciências, Universidade de Lisboa}
  \streetaddress{Campo Grande 016, 1749-016}
  \city{Lisbon}
  \country{Portugal}}
\email{mmgsilva@ciencias.ulisboa.pt}

\author{Rui Henriques}
\affiliation{%
  \institution{INESC-ID and Instituto Superior Técnico, Universidade de Lisboa}
  \streetaddress{Av. Rovisco Pais 1, 1900-001}
  \city{Lisbon}
  \country{Portugal}}
\email{rmch@tecnico.ulisboa.pt}

\author{Sara C. Madeira}
\affiliation{%
  \institution{LASIGE and Faculdade de Ciências, Universidade de Lisboa}
  \streetaddress{Campo Grande 016, 1749-016}
  \city{Lisbon}
  \country{Portugal}}
\email{sacmadeira@ciencias.ulisboa.pt}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Silva and Henriques, et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Collaborative Filtering (CF), the most common approach to build Recommender Systems, became pervasive in our daily lives as consumers of products and services. However, challenges limit the effectiveness of Collaborative Filtering approaches when dealing with recommendation data, mainly due to the diversity and locality of user preferences, structural sparsity of user-item ratings, subjectivity of rating scales, and increasingly high item dimensionality and user bases. To answer some of these challenges, some authors proposed successful approaches combining CF with Biclustering techniques.

This work assesses the effectiveness of Biclustering approaches for CF, comparing the impact of algorithmic choices, and identifies principles for superior Biclustering-based CF. As a result, we propose USBFC, a Biclustering-based CF approach that creates user-specific models from strongly coherent and statistically significant rating patterns, corresponding to subspaces of shared preferences across users. Evaluation on real-world data reveals that USBCF achieves competitive predictive accuracy against state-of-the-art CF methods. Moreover, USBFC successfully suppresses the main shortcomings of the previously proposed state-of-the-art biclustering-based CF by increasing coverage, and coclustering-based CF by strengthening subspace homogeneity. 
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10002951.10003227.10003351.10003269</concept_id>
       <concept_desc>Information systems~Collaborative filtering</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
   <concept>
       <concept_id>10002951.10003227.10003351.10003444</concept_id>
       <concept_desc>Information systems~Clustering</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
   <concept>
       <concept_id>10002951.10003317.10003347.10003350</concept_id>
       <concept_desc>Information systems~Recommender systems</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
 </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Information systems~Collaborative filtering}
\ccsdesc[500]{Information systems~Clustering}
\ccsdesc[500]{Information systems~Recommender systems}



%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{Collaborative Filtering, Biclustering, Pattern Discovery, Subspace Clustering, Recommender Systems}


%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\input{01introduction}
\input{02background}
\input{03relatedwork}
\input{04method}
\input{05results}
\input{06conclusion}



%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
\noindent This work was supported by the Fundação para a Ciência e a Tecnologia (FCT) under LASIGE strategic project (UIDB/00408/2020 and UIDP/00408/2020), iCare4U (PTDC/EME-SIS/31474/2017), WISDOM (DSAIPA/DS/0089/2018), ILU (DSAIPA/ DS/0111/2018) and INESC-ID (UIDB/50021/2020).
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{biclustering, biclusteringCF, collaborativefiltering}


\end{document}
\endinput
%%
%% End of file `sample-acmsmall-submission.tex'.
