\section{Evaluations}
\label{sec:evaluation}
Many speech processing works have collected or augmented datasets with real world sounds. Good solutions are usually then developed. But, in many cases the resultant datasets have limited in-the-wild sounds so where they actually work is limited, and many times the solutions are not validated in-the-wild, but only on the datasets. 

Our pre-deployment strategies are to significantly increase the collected and augmented datasets to increase comprehensiveness of the situations which are modeled, and specialize the datasets to a specific speech module (if needed).  In pre-deployment, we also choose a set of “best” solutions from the literature and using the comprehensive datasets, determine which ones work. If one or more off-the-shelf solution work, the best one is chosen. Below we show that often many off-the-shelf solutions do not work, but for many common speech tasks there are good solutions available, but it is necessary to verify that. We don’t want to reinvent the wheel. Then, in post deployment we validate the resulting performance on real data, a step often not performed.

Speech processing is typically performed in a pipeline depending on the overall purpose. In our system we need voice activity detection, speaker identification,  emotion detection, and conflict detection. There are commonalities and unique aspects to each of these stages so the pre-deployments strategies must account for them. We now consider each of these 4 stages in more detail. Specifically, we briefly reiterate what the components are, why they are important, and demonstrate what we did at pre-deployment time to maximize the deployment time success based on post-deployment data (how we evaluated them at pre-deployment time). In all cases the acoustic solutions had to address the real world complexities such as reverberation, deamplification, and the many types of noise found in real homes over long deployments. The relative success of the acoustic solutions (at the post-deployment time) confirms our hypothesis that it is possible to perform comprehensive and realistic pre-deployment testing to increase post deployment success.


\input{5_1_VAD}
\input{5_2_SID}
\input{5_3_mood}
\input{5_4_conflict}
\input{5_5_acoustic_summary}