\documentclass{cernyrep}
%\documentclass[superscriptaddress,a4paper]{revtex4}
%\documentclass[aps,superscriptaddress,letterpaper,nofootinbib]{revtex4}
%\documentclass[preprint,aps,superscriptaddress]{revtex4}
%\documentclass[12pt,tightenlines,aps,preprint,twocolumn,showpacs,nofootinbib,floatfix]{revtex4}
\usepackage[T1]{fontenc}
\usepackage[scale=.78]{geometry}

\usepackage{xspace}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{float}
\usepackage[nointegrals]{wasysym}
\usepackage{hyperref}
\usepackage{url}
\usepackage{subfig}
%
\usepackage{amsmath}
\usepackage[dvipsnames,usenames]{xcolor}
\usepackage{amssymb,array}
\usepackage{multirow}

% - Use the following four lines in the DRAFT mode
% \usepackage{draftwatermark}
% \SetWatermarkLightness{.9}
% \usepackage{lineno}
% \linenumbers

\hypersetup{
  linkcolor  = black, % tab of contents and eq/tab/fig links in text
  citecolor  = blue,
  urlcolor   = blue,
  colorlinks = true,
  breaklinks=true
}

%\documentstyle[tighten,aps,epsf,floats]{revtex}

%\usepackage{jheppub} 
%\usepackage[T1]{fontenc} 
\usepackage{placeins}
\usepackage{subfig}
\usepackage{adjustbox}
\usepackage{blindtext}
\usepackage{verbatim}
\usepackage{bm}
\usepackage[normalem]{ulem}
\usepackage[T1]{fontenc}

\newcommand{\OO}{\ensuremath{\mathcal{O}}}
\newcommand{\QQ}{\ensuremath{\mathcal{Q}}}
\newcommand{\pdp}{\ensuremath{\phi^\dagger\phi}}
\renewcommand{\phi}{\ensuremath{\varphi}}
\newcommand{\sss}{\scriptscriptstyle}
\newcommand{\sst}{\scriptstyle}
\newcommand{\Op}[1]{\OO_{\sss #1}}
\newcommand{\Opp}[2]{\OO_{\sss #1}^{\sss #2}}
\newcommand{\Qp}[1]{\QQ_{\sss #1}}
\newcommand{\Qpp}[2]{\QQ_{\sss #1}^{\sss #2}}
\newcommand{\lam}{\Lambda}
\newcommand{\cp}[1]{c_{\sss #1}}
\newcommand{\Cp}[1]{C_{\sss #1}}
\newcommand{\cpp}[2]{c_{\sss #1}^{\sss #2}}
\newcommand{\Cpp}[2]{C_{\sss #1}^{\sss #2}}
\def\lra#1{\overset{\text{\scriptsize$\leftrightarrow$}}{#1}}
\newcommand{\sw}{s_{\sss W}}
\newcommand{\cw}{c_{\sss W}}
\newcommand{\mw}{m_{\sss W}}
\newcommand{\mz}{m_{\sss Z}}
\newcommand{\mt}{m_{t}}
\input{Macros.tex}
\def\smallfrac#1#2{\hbox{$\frac{#1}{#2}$}}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\ben}{\begin{enumerate}}
\newcommand{\een}{\end{enumerate}}
\newcommand{\la}{\left\langle}
\newcommand{\ra}{\right\rangle}
\newcommand{\lc}{\left[}
\newcommand{\rc}{\right]}
\newcommand{\lp}{\left(}
\newcommand{\rp}{\right)}
\newcommand{\as}{\alpha_s}
\newcommand{\aq}{\alpha_s\left( Q^2 \right)}
\newcommand{\amz}{\alpha_s\left( M_Z^2 \right)}
\newcommand{\aqq}{\alpha_s \left( Q^2_0 \right)}
\newcommand{\aqz}{\alpha_s \left( Q^2_0 \right)}
\newcommand{\Ord}{\mathcal{O}}
\newcommand{\MSbar}{\overline{\text{MS}}}
\def\toinf#1{\mathrel{\mathop{\sim}\limits_{\scriptscriptstyle
{#1\rightarrow\infty }}}}
\def\tozero#1{\mathrel{\mathop{\sim}\limits_{\scriptscriptstyle
{#1\rightarrow0 }}}}
\def\toone#1{\mathrel{\mathop{\sim}\limits_{\scriptscriptstyle
{#1\rightarrow1 }}}}
\def\frac#1#2{{{#1}\over {#2}}}
\def\gsim{\gtrsim}
\def\lsim{\lesssim}
\newcommand{\mrexp}{\mathrm{exp}}
\newcommand{\dat}{\mathrm{dat}}
\newcommand{\one}{\mathrm{(1)}}
\newcommand{\two}{\mathrm{(2)}}
\newcommand{\art}{\mathrm{art}}
\newcommand{\rep}{\mathrm{rep}}
\newcommand{\net}{\mathrm{net}}
\newcommand{\stopp}{\mathrm{stop}}
\newcommand{\sys}{\mathrm{sys}}
\newcommand{\stat}{\mathrm{stat}}
\newcommand{\pdf}{\mathrm{pdf}}
\newcommand{\tot}{\mathrm{tot}}
\newcommand{\minn}{\mathrm{min}}
\newcommand{\mut}{\mathrm{mut}}
\newcommand{\partt}{\mathrm{part}}
\newcommand{\dof}{\mathrm{dof}}
\newcommand{\NS}{\mathrm{NS}}
\newcommand{\cov}{\mathrm{cov}}
\newcommand{\gen}{\mathrm{gen}}
\newcommand{\cut}{\mathrm{cut}}
\newcommand{\parr}{\mathrm{par}}
\newcommand{\val}{\mathrm{val}}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\checkk}{\mathrm{check}}
\newcommand{\reff}{\mathrm{ref}}
\newcommand{\Mll}{M_{ll}}
\newcommand{\extra}{\mathrm{extra}}
%\newcommand{\draft}[1]{}
\newcommand{\muf}{\mu_\text{F}}
\newcommand{\mur}{\mu_\text{R}}

\def\lra#1{\overset{\text{\scriptsize$\leftrightarrow$}}{#1}}

\newcommand{\fm}[1]{{\color{red}\bf #1}}

\newcommand{\TY}[1]{{\it \color{blue}[TY: #1]}}

\DeclareMathOperator{\Pois}{Pois}
\newcommand{\diff}{\mathrm{d}}


\usepackage{booktabs}
\usepackage{pifont}
\usepackage{cleveref}

\newcommand*\rot{\rotatebox{90}}



\begin{document}

\preprint{CERN-LHCEFTWG-2022-001\\ CERN-LPCC-2022-05}

\title{LHC EFT WG Report: Experimental Measurements and Observables}

\author{Nuno Castro\aff{LIP},
Kyle Cranmer\aff{Wis},
Andrei V. Gritsan\aff{JH},
James Howarth\aff{SUPA},
Giacomo Magni\twoaff{NIK}{VU},
Ken Mimasu\aff{King},
Juan Rojo\twoaff{NIK}{VU},
Jeffrey Roskes\aff{JH},
Eleni Vryonidou\aff{Man},
Tevong You\threeaff{TH-CERN}{AMTP}{Cav}
}

\institute{
\naff{LIP}{LIP, Departamento de F\'{i}sica, Escola de Ci\^{e}ncias, Universidade do Minho, 4710-057 Braga, Portugal}
\naff{Wis}{Department of Physics, University of Wisconsin, Madison, WI 53706, USA}
\naff{JH}{Department of Physics and  Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA}
\naff{SUPA}{SUPA - School of Physics and Astronomy, University of Glasgow, Glasgow, UK}
\naff{NIK}{Nikhef, Science Park 105, 1098 XG Amsterdam, The Netherlands}
\naff{VU}{Department of Physics and Astronomy, Vrije Universiteit, NL-1081 HV Amsterdam, The Netherlands}
\naff{King}{Department of Physics, King's College London, Strand, London WC2R 2LS, UK}
\naff{Man}{Department of Physics and Astronomy, University of Manchester, Oxford Road, Manchester M13 9PL, UK}
\naff{TH-CERN}{Theoretical Physics Department, CERN, CH-1211 Geneva 23, Switzerland}
\naff{AMTP}{AMTP, University of Cambridge, Wilberforce Road, Cambridge CB3 0WA, UK}
\naff{Cav}{Cavendish Laboratory, University of Cambridge, J.J. Thomson Avenue, Cambridge CB3 0HE, UK}
}

\date{November 15, 2022}
%\date{\today}

\begin{abstract}
The LHC effective field theory working group gathers members of the LHC experiments and the theory community 
to provide a framework for the interpretation of LHC data in the context of EFT. In this note we discuss experimental 
observables and corresponding measurements in analysis of the Higgs, top, and electroweak data at the LHC. 
We review the relationship between operators and measurements relevant for the interpretation 
of experimental data in the context of a global SMEFT analysis.
One of the goals of ongoing effort is bridging the gap between theory and experimental communities 
working on EFT, and in particular concerning optimised analyses.
This note serves as a guide to experimental measurements and observables leading to EFT fits 
and establishes good practice, but does not present authoritative guidelines how those measurements 
should be performed. 
\end{abstract}

\maketitle

\setcounter{tocdepth}{3}
\tableofcontents

\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Introduction}
\label{sect:area3_intro}
\input{area3-intro.tex}

\section{Experimental observables and corresponding measurements}
\label{sect:area3_observables}
\input{area3-observables.tex}

\clearpage

\section{Operators and measurements for global SMEFT fits}
\label{sect:area3_operators}
\input{area3-operators.tex}

\clearpage

\section{Summary}
\label{sect:summary}

This note serves as a guide to experimental measurements and observables leading to EFT fits, but does not establish 
authoritative guidelines how those measurements should be performed. There is a spectrum of approaches to 
experimental measurements and observables, each approach has its own stronger and weaker sides, 
and none of the approaches has been established as the universally best approach to perform the EFT measurements. 
Analysis of LHC data in the framework of global EFT approach is a relative young field at this point. It has evolved 
from the less demanding task of interpreting of LHC data in the framework of standard model and of testing for
its deviations in individual measurements. The field is still actively evolving, and the numbers of parameters and
channels to be analyzed in an optimal and unbiased way are enormous. This poses both technical and 
conceptual challenges in performing the measurements, which will be resolved only gradually in close
collaboration of experimental and theoretical particle physicists. 
One of the goals of ongoing effort is bridging the gap between theory and experimental communities working on EFT, 
and in particular concerning optimised analyses that so far are only accessible within the experiment.

The types of observables range from the usual quantities calculated for the SM measurements, 
to the EFT-sensitive observables, and to the optimized observables utilizing advanced matrix-element 
and machine-learning techniques. Good sensitivity to EFT effects is desired when constructing an observable. 
The single-step measurement approach allows extraction of EFT parameters from the data directly without intermediate results. 
This approach is conceptually straightforward, unbiased, can be an optimal approach, but suffers from complexity 
and the lack of re-interpretation capability. The two-step measurement approach allows wide dissemination and 
preservation of the data in the form of differential truth-level distribution (first step) for later re-interpretation
(second step), but potentially this may lead to a non-optimal and/or biased analysis if care is not taken to 
address these concerns. Reporting the measurement results may represent a challenge on its own, 
as reporting the full likelihood function would be the ideal outcome and would allow interpretation 
and combination with other results. However, treatment of parameters with weak constraints and 
of systematic uncertainties, which may be correlated with other measurements, may complicate this process. 
This note does not provide specific guidelines how these issues should be technically addressed, 
but points to their importance.

In the second part of the note, we presented the main aspects of the mapping between observables and operators 
in the context of global SMEFT interpretations, in the specific cases of two global fit efforts. 
The set of operators considered in different flavour assumptions has been presented as well as a discussion of the 
set of measurements which have been used to constrain these operators. The sensitivity of different observables 
to different operators in the flavour universal scenario is quantified by examining the linear dependencies of Higgs, 
diboson, and electroweak measurements obtained in the \verb|fitmaker| analysis. 
This allows the results of individual or marginalised constraints from global fits to be understood more intuitively. 
Similarly, a detailed analysis based on the Fisher information formalism can be used to explore the relative sensitivity 
of various observables to the EFT operators as presented in the SMEFiT analysis. 
In the results of a global fit, the question also naturally arises as to which measurement is responsible for setting 
the strongest constraints. In this note this decomposition is shown for individual constraints. 
It has been observed that in order to understand the relation between operators and measurements, 
a single tool is often not sufficient, and that the whole picture only comes together by comparing the output 
of complementary tools. For example, the Fisher information is powerful, but in some cases only a direct fit 
with some specific datasets omitted provides the necessary insight. 
Finally results of the global fit have been shown. 

\bigskip

\noindent
{\bf Acknowledgments}:
%
This work was done on behalf of the LHC EFT WG and 
we would like to thank members of the LHC EFT WG for stimulating discussion of experimental measurements
and observables which led to this document. 
%

%\clearpage

%------------------------------------------------------------------------------------------------------------------------------

% References: use option 1 to create references, use option 2 when references are stable 
% option 1: use BIBTEX, see for style help: http://arxiv.org/hypertex/bibstyles/
%\bibliographystyle{JHEP}
%\bibliography{lhceftwg3}
% option 2: use direct bbl file generated by BIBTEX instead of BIBTEX
\input{area3.bbl}

%-----------------------------------------------------------------------
\end{document}
%-----------------------------------------------------------------------


