% \documentclass[a4,center,fleqn]{NAR}
% \documentclass[acmsmall]{acmart}[12pt]
\documentclass[camera,hyphens]{jpaper}
\input{packages}
\input{commands}

% Enter dates of publication
% \copyrightyear{YYYY}
% \pubdate{DD MM YYYY}
% \pubyear{YYYY}
% \jvolume{xx}
% \jissue{xx}

% %\articlesubtype{This is the article type (optional)}
% \newcites{supp}{Supplementary References}
% \setlength{\skip\footins}{1.2pc plus 10pt minus 2pt}
% \setlength{\footnotesep}{2pc}

\begin{document}

\title{\ltitle}



\maketitle
\def\thefootnote{*}\footnotetext{These authors contributed equally to this work.}\def\thefootnote{\arabic{footnote}}
\input{sections/0_abstract}
\input{sections/1_introduction}
\input{sections/2_methods}
\input{sections/results}
% \input{sections/motivation}
\input{sections/4_discussion}
\input{sections/3_evaluation}

% \input{sections/5_conclusion}

\section{Data Availability}

The read set used in this study was downloaded from \url{https://bridges.monash.edu/articles/dataset/Raw_fast5s/7676174}, while the reference set can be downloaded from  \url{https://bridges.monash.edu/articles/dataset/Reference_genomes/7676135}. We use the official ONT dataset~\cite{bonito} for training and evaluating all our models. 
% We make the real and simulated datasets we use available on the Zenodo website. For the human genome dataset, we download the data from the EBI website. We provide the accession numbers of all the public datasets we use in Table~\ref{tab:dataset}. We provide all the scripts 1) with the Zenodo links to download both real and simulated datasets and 2) to fully reproduce our results and figures. These scripts are available at \href{https://github.com/CMU-SAFARI/BLEND/tree/master/test}{https://github.com/CMU-SAFARI/BLEND/tree/master/test}, which also includes instructions to use these scripts.
% \sr{
\section{Code Availability}
Scripts used to perform basecalling accuracy analysis are available at: \url{https://github.com/rrwick/Basecalling-comparison}.
Source code, including pre-trained models, scripts to generate basecalled reads, and reproducible results instruction, will be made publicly available upon publication. %We will make it publicly available upon publication.
%https://github.com/CMU-SAFARI/RUBICON.


\section{Acknowledgments}
\gsssss{We thank the SAFARI Research Group members for their valuable feedback and the stimulating intellectual \gssssss{and} scholarly environment they provide. SAFARI Research Group acknowledges the generous gifts of our industrial partners, including Google, Huawei, Intel, Microsoft, VMware, and Xilinx. This research was partially supported by the Semiconductor Research Corporation.}
 Special thanks to  Alessandro Pappalardo for his support with quantization-aware training. We appreciate valuable discussions with Giovanni Mariani.  Thanks to AMD for providing access to the HPC fund cluster~\cite{hpcfund}. %We thank the SAFARI Research Group members for valuable feedback and the stimulating intellectual environment they provide. 

% \section{Author Contributions}
% XXX conceived of the presented idea. XXX implemented the tool. XXX collected data. XXX produced the figures. XXX performed the evaluations. All authors wrote, reviewed, and edited the manuscript. All authors discussed the text and commented on the manuscript. All authors read and approved the final manuscript. 

\section{Competing Interests} 
All authors declare no competing interests.

% \section{Funding}
% O.M. and SAFARI Research Group are supported by funding from Intel, VMware, Semiconductor Research Corporation, the National Institutes of Health (NIH), and the ETH Future Computing Laboratory.
% % }


\newpage
\balance
\bibliographystyle{IEEEtranS}

{\small \bibliography{ref}}

\input{sections/supp}

\end{document}
