\documentclass[preprint,1p,times,longtitle]{elsarticle}

\usepackage[utf8x]{inputenc}
\usepackage{cite}
\usepackage{url}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\usepackage[nolist]{acronym}
\usepackage{todonotes}
\usepackage{dirtytalk}
\usepackage{multirow}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{hyperref}


\usepackage[T1]{fontenc}
\usepackage[scaled=0.9]{beramono}
\usepackage{microtype}

\newcommand\Small{\fontsize{8}{10}\selectfont}
\newcommand*\LSTfont{%
  \Small\ttfamily\SetTracking{encoding=*}{-50}\lsstyle}

\lstset{
  basicstyle=\LSTfont,
  columns=fullflexible,
  xleftmargin=5mm,
  framexleftmargin=5mm,
  breakatwhitespace=false,
  tabsize=2,
  captionpos=b,
  numbers=left,
  frame=shadowbox
}

\presetkeys{todonotes}{fancyline,color=green}{}

\newcommand{\cm}[1]{\todo[author=Comentario Álvaro,color=orange]{#1}}

\newcommand{\oslc}[1]{\emph{oslc:#1}}
\newcommand{\trs}[1]{\emph{trs:#1}}
\newcommand{\auto}[1]{\emph{oslc\_auto:#1}}
\newcommand{\oslccm}[1]{\emph{oslc\_cm:#1}}
\newcommand{\actions}[1]{\emph{oslc\_eca:#1}}
\newcommand{\events}[1]{\emph{oslc\_eca:#1}}
\newcommand{\ewe}[1]{\emph{ewe:#1}}
\newcommand{\kafka}[1]{\emph{kafka:#1}}
\newcommand{\eca}[1]{\emph{oslc\_eca:#1}}

\hyphenation{Ser-vice-Pro-vi-der}
\hyphenation{Au-to-ma-tion-Plan}
\hyphenation{Au-to-ma-tion-Re-quest}
\hyphenation{Au-to-ma-tion-Re-sult}

\newpageafter{author}

\begin{document}

\begin{frontmatter}

%\title{Towards an architecture for automation of DevOps based on the OSLC standard}
%\title{Extension of OSLC standard for ECA model}
%\title{Including Events and Actions in OSLC standard for ECA-based automation}
%\title{Extending OSLC automation domain for ECA-based automation}
%\title{Extending OSLC standard for ECA-based DevOps automation}
\title{Extending the OSLC standard for ECA-based automation in DevOps environments}


% \author{\IEEEauthorblockN{Guillermo García Grao}}
\author[gsi]{Guillermo García-Grao\corref{cor1}}
\ead{g.ggrao@upm.es}

\author[gsi]{Álvaro Carrera}
\ead{a.carrera@upm.es}

\cortext[cor1]{Corresponding author}
\address[gsi]{Universidad Politécnica de Madrid, Avenida Complutense 30, Ciudad Universitaria, 28040, Madrid}

% \maketitle

\begin{abstract}

The DevOps paradigm is taking over software development systems, helping businesses increase efficiency, accelerate production, and adapt quickly to market changes.
However, adopting these principles can be challenging.
Practitioners often face an important issue known as vendor lock-in caused by the cost of tool replacement.
In addition, automating the processes that involve these tools also requires investment.
These issues could be addressed by standardizing service interfaces to facilitate their integration.
Linked Data is an attractive choice for implementing such a standard without sacrificing versatility.
An exciting and promising proposal in this direction is the \ac{OSLC} standard specification.
Its purpose is to build an environment where services can interoperate using standard Linked Data models.
However, the current specification version still lacks standard definitions for concepts that are critical to automating the execution of actions in fast-changing environments.
Therefore, this paper proposes a new specification to extend \ac*{OSLC}, based on the \ac*{ECA} model, for event-based interoperable automation, especially for DevOps environments, which are our motivational scenario.
A simple DevOps architecture is built as a prototype to validate the proposed model.
Using that architecture, the proposed model is validated in a real-world workflow to prove its contribution to the OSLC standard and the DevOps field.
% The architecture and the \ac*{OSLC} extension are the main contributions presented in this work.
% Finally, a case study is implemented to demonstrate how the proposal addresses the described challenges in adopting DevOps practices.

\end{abstract}

% \begin{IEEEkeywords}
\begin{keyword}
OSLC \sep DevOps \sep Linked Data \sep semantic \sep ontology \sep rule-based automation
\end{keyword}
% \end{IEEEkeywords}

\end{frontmatter}

\begin{acronym}
 
 \acro{OWL}[OWL]{Web Ontology Language} 
 \acro{RDF}[RDF]{Resource Description Framework}
 \acro{RDFS}[RDFS]{Resource Description Framework Schema}
 \acro{OSLC}[OSLC]{Open Services for Lifecycle Collaboration}
 \acro{EWE}[EWE]{Evented WEb}
 \acro{TAS}[TAS]{Task Automation Server}
 \acro{ECA}[ECA]{Event-Condition-Action}
 \acro{AaaS}[AaaS]{Automation as a Service}
 \acro{W3C}[W3C]{World Wide Web Consortium}
 \acro{MQTT}[MQTT]{Message Queuing Telemetry Transport}
 \acro{TRS}[TRS]{Tracked Resource Set}
 \acro{EYE}[EYE]{Euler Yet another proof Engine}
 \acro{CAD}[CAD]{Computer-Aided Design}
 \acro{BPMN}[BPMN]{Business Process Modeling Notation}
 \acro{CRUD}[CRUD]{Create, Read, Update and Delete}
 \acro{FOL}[FOL]{First Order Logic}
 \acro{CI}[CI]{Continuous Integration}
 \acro{DML}[DML]{Distributed Messaging Layer}

\end{acronym}

\section*{Acknowledgment}

This research work is supported by the Ministry of Science and Innovation (Spain) through the SmartDevOps project (RTC2019-007326-7). 

\input{1-introduction.tex}
\input{2-related_work.tex}
\input{3-background.tex}
\input{4-semantic_model.tex}
\input{5-evaluation.tex}
\input{6-conclusions_and_future_work.tex}
% \input{problem_overview.tex}
% \input{architecture.tex}
% \input{case_study.tex}
% \input{evaluation.tex}


% \bibliographystyle{elsarticle-harv}
% \bibliography{introduction,state_of_the_art,problem_overview,semantic_model,architecture,case_study,evaluation,conclusion}
\bibliography{references}
\bibliographystyle{plainnat}


\end{document}
