\documentclass[runningheads]{comsis2}

%% Necessary definitions for the running heads
\def\journalissue{}
\def\paperidnum{}
\setcounter{page}{1}
\usepackage[square,numbers]{natbib} % has a nice set of citation styles and commands
    \bibliographystyle{abbrvnat}
    \renewcommand{\bibsection}{\subsection*{References}}
%% Use this to show line numbers (and remove only in the final camera-ready version)
\usepackage{geometry}
\geometry{
  a4paper,         % or letterpaper
  textwidth=17cm,  % llncs has 12.2cm
  textheight=24cm, % llncs has 19.3cm
  heightrounded,   % integer number of lines
  hratio=1:1,      % horizontally centered
  vratio=2:3,      % not vertically centered
  }
\usepackage[colorlinks=true,bookmarks=true,citecolor=blue,urlcolor=blue]{hyperref} %pdflatex
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{booktabs} % for professional tables
\usepackage{paralist}
\usepackage{soul}
\usepackage{algorithmic}
\usepackage[linesnumbered,lined,boxed,commentsnumbered,ruled,vlined]{algorithm2e}
\newcommand{\theHalgorithm}{\arabic{algorithm}}
\usepackage{float}
\usepackage[british]{babel}
% For theorems and such
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{stackrel}
\usepackage{apxproof}
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{xcolor}         % colors
\usepackage{mathptmx}
\usepackage{dsfont}
\usepackage[title]{appendix}
\usepackage{multirow}
\usepackage{wrapfig}
% Recover regular caligraphic letters
\DeclareMathAlphabet{\mathcal}{OMS}{cmsy}{m}{n}
%\usepackage{multicol}
\usepackage{tabularx}
\usepackage{bm}
\usepackage{tikz} 
\tikzset{
  agent/.style={draw, circle, minimum size=2mm,
  font=\footnotesize},
  x = 1.5cm, y=1.5cm,
  every loop/.style={},
  block/.style={draw, rectangle, minimum height=3em, minimum width=6em},
}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{positioning}
\usetikzlibrary{shapes,arrows,matrix,scopes,shadows,chains,automata,positioning,fit, arrows.meta,calc}


% if you use cleveref..
\usepackage[capitalize,noabbrev]{cleveref}
\usepackage{libertine}
% \linenumbers
\usepackage{notation}
\crefname{subsection}{subsection}{subsections}
\crefname{lemma}{lemma}{lemma}
\crefname{property}{property}{property}
\crefname{table}{table}{table}
\crefname{assumption}{assumption}{assumption}
\crefname{table}{table}{tables}
\Crefname{table}{Table}{Tables}
\crefname{figure}{Fig.}{Fig.}
\Crefname{figure}{Fig.}{Fig.}
% \theoremstyle{plain}
% \newtheorem{property}{Property}[section]
\renewcommand\theproperty{(P\arabic{property})}
\newtheorem{assumption}[theorem]{Assumption}
\title{On learning history based policies for controlling Markov decision processes}
% \footnote{If this is an extended version of a conference paper, it should be clearly stated here.}
%% Use this if the title is too long for the running heads
\titlerunning{On learning history based policies for controlling Markov decision processes}

\author{Gandharv Patil\inst{1} \and Aditya Mahajan\inst{1} \and Doina Precup\inst{1}}

%% Use this the list of authors is too long for the running heads
%\authorrunning{First Author et al.}

\institute{McGill University,  Mila\\
  Montreal QC - Canada\\
  \email{gandharv.patil@mail.mcgill.ca,  aditya.mahajan@mcgill.ca,  dprecup@cs.mcgill.ca}}
%   \and
%   Faculty of the Second Author\\
%   Address\\
%   \email{author2@faculty.edu}}

\begin{document}

\maketitle

\begin{abstract}
Reinforcement learning (RL) folklore suggests that history-based function approximation methods, such as recurrent neural nets or history-based state abstraction, perform better than their memory-less counterparts, due to the fact that function approximation in Markov decision processes (MDP) can be viewed as inducing a Partially observable MDP. However, there has been little formal analysis of such history-based algorithms, as most existing frameworks focus exclusively on memory-less features. In this paper, we introduce a theoretical framework for studying the behaviour of RL algorithms that learn to control an MDP using history-based feature abstraction mappings. Furthermore, we use this framework to design a practical RL algorithm and we numerically evaluate its effectiveness on a set of continuous control tasks. 


\end{abstract}

\input{sections/introduction}
\input{sections/model2}
\input{sections/algorithm-a}
\input{sections/results-new}
\input{sections/relatedwork}
\input{sections/conclusion}

% \bibliographystyle{splncs03}
\bibliography{references}

\appendix
\pagenumbering{arabic}
\section*{Appendix}
\input{sections/appendix}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% For the final version of the paper: %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Author information
%\vspace{4ex}\noindent
%\textbf{Author One} is\dots
%
%\bigskip\noindent
%\textbf{Author Two} is\dots
%
%\bigskip\noindent
%\textbf{Author Three} is\dots

%% Reception and acceptance information
%\bigskip
%\paragraph{Received: Month DD, 20YY; Accepted: Month DD, 20YY.}

\end{document}
