% This must be in the first 5 lines to tell arXiv to use pdfLaTeX, which is strongly recommended.
\pdfoutput=1
% In particular, the hyperref package requires pdfLaTeX in order to break URLs across lines.

\documentclass[11pt]{article}

% Remove the "review" option to generate the final version.
\usepackage[]{EMNLP2022}

% Standard package includes
\usepackage{times}
\usepackage{mathtools}
\usepackage{latexsym}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{url}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{xspace}
%TODO
\usepackage{verbatim}
\usepackage{CJKutf8}
\usepackage{multirow}
\usepackage{tabularx}


\usepackage{array}
\usepackage{adjustbox}
\usepackage{booktabs}
\usepackage{amsthm}
\usepackage{subcaption}
\usepackage{algorithm}
\usepackage{algpseudocode}
% \usepackage{algorithmicx}
% \usepackage{algorithm}
\newcommand\BibTeX{B\textsc{ib}\TeX}
\usepackage{color}
\usepackage{colortbl}
\usepackage{xcolor}
\usepackage{relsize}
\usepackage{cleveref}
\usepackage{bbm}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{soul}
\usepackage{algorithmicx}
\usepackage{algorithm}
\usepackage{xspace}
\newcolumntype{b}{X}
\newcolumntype{s}{>{\hsize=.5\hsize}X}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\definecolor{RED}{RGB}{255,0,0}
\definecolor{GREEN}{RGB}{0,172,78}
\newcommand{\thetav}{{\boldsymbol \theta}}
\newcommand{\hlc}[2][yellow]{{%
		\colorlet{foo}{#1}%
		\sethlcolor{foo}\hl{#2}}%
}
% \definecolor{Red}{red}{0.8}
% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
\usepackage[T1]{fontenc}
% For Vietnamese characters
% \usepackage[T5]{fontenc}
% See https://www.latex-project.org/help/documentation/encguide.pdf for other character sets

% This assumes your files are encoded as UTF8
\usepackage[utf8]{inputenc}
\newcommand{\approach}{\textsc{REGEX}}
% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}
\newcommand\integratedgrads{\textit{IG}}
\newcommand{\synteq}{::=}
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
% If the title and author information does not fit in the area allocated, uncomment the following
%
%\setlength\titlebox{<dim>}
%
% and set <dim> to something 5cm or larger.

% \title{Calibration Meets Explanation:\\ How Can We Get Better Model Confidence?}
\title{Calibration Meets Explanation: \\
A Simple and Effective Approach for Model Confidence Estimates}
\author{Dongfang Li$^1$, Baotian Hu$^1$\footnotemark[1]\thanks{\hspace{2mm}Corresponding authors}\hspace{2mm},  Qingcai Chen$^{1,2}$\footnotemark[1]\hspace{1mm}\\
$^1$Harbin Institute of Technology (Shenzhen), Shenzhen, China \\
$^2$Peng Cheng Laboratory, Shenzhen, China\\
\texttt{crazyofapple@gmail.com, \{hubaotian, qingcai.chen\}@hit.edu.cn}}
\begin{document}
\maketitle
\begin{abstract}

Calibration strengthens the trustworthiness of black-box models by producing better accurate confidence estimates on given examples. However, little is known about if model explanations can help confidence calibration. Intuitively, humans look at important features attributions and decide whether the model is trustworthy. Similarly, the explanations can tell us when the model may or may not know. Inspired by this, we propose a method named \textbf{CME} that leverages model explanations to make the model less confident with non-inductive attributions. The idea is that when the model is not highly confident, it is difficult to identify strong indications of any class, and the tokens accordingly do not have high attribution scores for any class and vice versa. We conduct extensive experiments on six datasets with two popular pre-trained language models in the in-domain and out-of-domain settings. The results show that CME improves calibration performance in all settings. The expected calibration errors are further reduced when combined with temperature scaling. Our findings highlight that model explanations can help calibrate posterior estimates.


\end{abstract}

\input{intro}


\input{method}

\input{experiment}
\input{conclusion}



% Entries for the entire Anthology, followed by custom entries
\bibliography{anthology,custom}
\bibliographystyle{acl_natbib}
\clearpage
\input{appendix}


\end{document}