\null\skip0.2in
\begin{center}
{\bf \Large \underline{Competition Awards}}
\end{center}
\vspace{12mm}
% (* denotes equal contribution)
\begin{enumerate}[leftmargin=*]

\item {Asian Dean's Forum 2022 – The Rising Stars Women in Engineering Workshop} \hfill {2022}
\\ \textit{shortlisted participant} (https://risingstarsasia.org/index.php)

\item {2nd Dial2Doc Workshop \textbf{Best Student Paper Award}} \hfill {2022}
\\"Retrieval-Free Knowledge-Grounded Dialogue Response Generation with Adapters". 
\\Yan XU, Etsuko, Samuel Cahyawijaya, Zihan Liu, Genta Indra, Andrea Madotto, \textbf{Dan Su}, Pascale Fung

 \item {\textbf{Top-1} on KILT Leaderboard} \hfill {2021}
% \\ "Read before Generate! Faithful Long Form Question Answering with Machine Reading".
\\KILT is a public leaderboard organized by researchers from Facebook AI, for knowledge intensive NLP tasks.
 \\\textbf{Leaderboard Top-1} on the open-domain QA task. (\textbf{1-person team})
\\(\url{https://eval.ai/web/challenges/challenge-page/689/leaderboard/1908}).

\item {\textbf{Top-1} on Computational Linguistics Lay Summary Challenge
} \hfill {2020}\\
% \\\textbf{1st place winner}. \\
"Dimsum @LaySumm 20: BART-based Approach for Scientific Document Summarization" \\
(\url{https://competitions.codalab.org/competitions/25516#participate})

\item {\textbf{1st Place Winner} Kaggle COVID-19 Open Research Dataset Challenge (\href{https://www.kaggle.com/allen-institute-for-ai/CORD-19-research-challenge/tasks}{CORD-19})} \hfill {2020}
\\An AI challenge organized by AllenAI, Chan Zuckerberg Initiative, The White House ect. \\\textbf{1st place winner} (\textbf{team leader}) on task 10, out of > 500 international teams, received \$1000 from the organizer.
(\url{https://www.kaggle.com/datasets/allen-institute-for-ai/CORD-19-research-challenge/discussion/148807})
 \item {\textbf{1st Place Winner} Chatbot Millionaire Challenge} \hfill 2019
\\In "AI+U: Explore and Experience Exhibition", organized by Hong Kong Science \& Technology Park. 
\\\textbf{1st place winner} (\textbf{team leader}), received a prize of HK\$30,000.
(\url{https://www.hkstp.org/press-room/hkstp-s-aiplusu-explore-and-
experience-exhibition-brings-together-the-ai-community-to-charter-next-path-of-growth/})

 \item {Machine Reading for Question Answering (MRQA) 2019 Shared Task} \hfill 2019
\\Ranked \textbf{4/10} among all, including industry competitors like Baidu Inc.(1st), Apple Inc.(2nd). (\textbf{team leader})

\end{enumerate}

