% !TeX document-id = {40781491-61d6-4729-a64a-d7388d4ec411}
% !TeX TXS-program:bibliography = txs:///biber

\newif\ifarxiv\arxivtrue
\newif\ifec\ecfalse
\newif\ifanonymous\anonymousfalse
\newif\ifdraft\draftfalse


\documentclass[a4paper,11pt]{scrartcl}

\input{header}
	
\ifdraft
	%draft-options:
	\usepackage[left=1cm, right=5cm, top=2cm, bottom=4cm]{geometry}
	\usepackage[ngerman, textsize=small, textwidth=4.5cm, color=lightgray]{todonotes}
	\definecolor{darkgreen}{rgb}{0.2,0.8,0.55}
	\definecolor{aliceblue}{rgb}{0.8, 0.9, 1.0}
	% Darf erst nach dem Einbinden von todonotes erstellt werden (alternativ - tikz einbinden...)
	\newcommand{\tobias}[1]{\todo[color=red,size=small]{Tobias: #1}}
	\newcommand{\lukas}[1]{\todo[color=aliceblue,size=small]{Lukas: #1}}
	\newcommand{\lukasI}[1]{\todo[color=aliceblue,inline]{Lukas: #1}}
\else 
	\usepackage[left=3cm, right=3cm, top=2cm, bottom=4cm]{geometry}
	\newcommand{\tobias}[1]{\relax}
	\newcommand{\lukas}[1]{\relax}
	\newcommand{\lukasI}[1]{\relax}
\fi

\title{Side-Constrained Dynamic Traffic Equilibria}
\author{Lukas Graf and Tobias Harks}

\date{}

\newcommand{\revised}[2][]{#2}

\newcommand{\abstracttext}{%
	We study  dynamic traffic assignment with side-constraints.
	We first give a counterexample to a key result from the literature
	regarding the existence of dynamic equilibria
	for volume-constrained traffic models in the classical linear edge-delay model. Our counterexample shows
	that the feasible flow space need not be convex and it further reveals
	that classical infinite dimensional variational inequalities are not suited for the definition of general side-constrained dynamic equilibria. We propose a new framework for side-constrained dynamic  equilibria
	based on the concept of \addmEpsDev s of flow particles in space and time. We then show under which assumptions the resulting equilibria can still be characterized by means of quasi-variational and variational inequalities, respectively.
	Finally, we establish first existence results for side-constrained dynamic equilibria for the non-convex setting of volume-constraints.%
}
\newcommand{\acknowledgetext}{%
	We thank Patrice Marcotte and Renxin Zhong as well as the anonymous reviewers for their helpful comments on an earlier version of this paper. We also thank Julian Schwarz, Michael Markl, David Watling and Michael Smith for many interesting discussions on the topics of this paper.%
}

\addbibresource{master-bib.bib}

\begin{document}
	
\thispagestyle{empty}
\maketitle

%\begin{center}
%	Draft
%\end{center}

\begin{abstract}
	\abstracttext
\end{abstract}

\newpage
\tableofcontents
\newpage

\input{chapters/Introduction}

\input{chapters/StaticModel}

\input{chapters/DynamicFlows}

\input{chapters/CounterExample}

\input{chapters/EquilibriumDefinition}

\input{chapters/Characterization}

\input{chapters/SCviaNetworkLoading}

\input{chapters/ExistenceResults}

\input{chapters/Conclusion}

\paragraph*{Acknowledgments:} \acknowledgetext


\clearpage
\printbibliography
\clearpage

\appendix

\input{chapters/ListOfSymbols}

\input{chapters/AdditionalExamples}

\input{chapters/VI-Solution-Existence}

\end{document}
