% \documentclass[a4,center,fleqn]{NAR}
% \documentclass[acmsmall]{acmart}[12pt]
\documentclass[camera,hyphens]{jpaper}
\input{packages}
\input{commands}

% Enter dates of publication
% \copyrightyear{YYYY}
% \pubdate{DD MM YYYY}
% \pubyear{YYYY}
% \jvolume{xx}
% \jissue{xx}

% %\articlesubtype{This is the article type (optional)}
% \newcites{supp}{Supplementary References}
% \setlength{\skip\footins}{1.2pc plus 10pt minus 2pt}
% \setlength{\footnotesep}{2pc}

\begin{document}

\title{\ltitle}



\maketitle
\def\thefootnote{*}\footnotetext{These authors contributed equally to this work.}\def\thefootnote{\arabic{footnote}}
\input{sections/0_abstract}
\input{sections/1_introduction}
\input{sections/2_methods}
\input{sections/results}
% \input{sections/motivation}
\input{sections/4_discussion}
\input{sections/3_evaluation}

% \input{sections/5_conclusion}

\section{Data Availability}

The read set used in this study was downloaded from \url{https://bridges.monash.edu/articles/dataset/Raw_fast5s/7676174}, while the reference set can be downloaded from  \url{https://bridges.monash.edu/articles/dataset/Reference_genomes/7676135}. 
We use the official ONT dataset~\cite{bonito} for training and evaluating all our models. 


\section{Code Availability}
Source code with the instructions for reproducing the results will be made publicly available upon publication. Scripts used to perform basecalling accuracy analysis are available at: \url{https://github.com/rrwick/Basecalling-comparison}.



\section{Acknowledgments}
\gsssss{We thank the SAFARI Research Group members for their valuable feedback and the stimulating intellectual \gssssss{and} scholarly environment they provide. SAFARI Research Group acknowledges the generous gifts of our industrial partners, including Google, Huawei, Intel, Microsoft, VMware, and Xilinx. This research was partially supported by the Semiconductor Research Corporation.}
 Special thanks to  Alessandro Pappalardo for his support with quantization-aware training. We appreciate valuable discussions with Giovanni Mariani.  Thanks to AMD for providing access to the HPC fund cluster~\cite{hpcfund}. %We thank 

\section{Competing Interests} 
All authors declare no competing interests.

\newpage
\balance
\bibliographystyle{IEEEtranS}

{\small \bibliography{ref}}

\input{sections/supp}

\end{document}
