\documentclass{article}

\PassOptionsToPackage{numbers, compress}{natbib}
\usepackage[final]{neurips_2020}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{mathtools}
\usepackage{enumitem}

\usepackage{bm}

\usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}

\title{FinRL-Meta: Market Environments and Benchmarks for Data-Driven Financial Reinforcement Learning}

\author{%
  Xiao-Yang Liu$^{1*}$, Ziyi Xia$^1\thanks{Equal contribution.}$ , Jingyang Rui$^2$, Jiechao Gao$^3$, Hongyang Yang$^1$, \\ \textbf{Ming Zhu$^4$, Christina Dan Wang$^{5\dagger}$, Zhaoran Wang$^6$, Jian Guo$^7 $\thanks{Corresponding authors.}}\\
  $^1$Columbia University; $^2$The University of Hongkong; $^3$University of Virginia; \\$^4$SIAT CAS; $^5$New York University (Shanghai); $^6$Northwestern University; \\$^7$IDEA Research, International Digital Economy Academy\\
  \texttt{\{xl2427, zx2325, hy2500\}@columbia.edu, christina.wang@nyu.edu,} \\
  \texttt{zhaoranwang@northwestern.edu, guojian@idea.edu.cn}\\
}


\begin{document}

\maketitle

\begin{abstract}
  Finance is a particularly difficult playground for deep reinforcement learning. However, establishing high-quality market environments and benchmarks for financial reinforcement learning is challenging due to three major factors, namely, low signal-to-noise ratio of financial data, survivorship bias of historical data, and model overfitting in the backtesting stage. In this paper, we present an openly accessible FinRL-Meta library that has been actively maintained by the AI4Finance community. First, following a DataOps paradigm, we will provide hundreds of market environments through an automatic pipeline that collects dynamic datasets from real-world markets and processes them into gym-style market environments. Second, we reproduce popular papers as stepping stones for users to design new trading strategies. We also deploy the library on cloud platforms so that users can visualize their own results and assess the relative performance via community-wise competitions. Third, FinRL-Meta provides tens of Jupyter/Python demos organized into a curriculum and a documentation website to serve the rapidly growing community. FinRL-Meta is available at: \url{https://github.com/AI4Finance-Foundation/FinRL-Meta} 
\end{abstract}


\input{NeurIPS_2020_version/Section1_Introduction}


\input{NeurIPS_2020_version/Section2_ExistingWorks}


\input{NeurIPS_2020_version/Section3_Architecture}


\input{NeurIPS_2020_version/Section3_Environment}


\input{NeurIPS_2020_version/Section4_Evaluation}




\section{Conclusion}

In this paper, we obeyed the DataOps paradigm and developed a FinRL-Meta library that provides openly accessible dynamic financial datasets and reproducible benchmarks. For future work, FinRL-Meta aims to build a universe of financial market environments, like the XLand environment \cite{team2021open}. To improve the performance for the large-scale markets, we are exploiting GPU-based massive parallel simulation such as Isaac Gym \cite{makoviychuk2021isaac}. Moreover, it will be interesting to explore the evolutionary perspectives \cite{gupta2021embodied,scholl2021market,finrl_podracer_2021, liu2021podracer} to simulate the markets. We believe that FinRL-Meta will provide insights into complex market phenomena and offer guidance for financial regulations.



\section*{Acknowledgement}

We thank Mr. Tao Liu (IDEA Research, International Digital Economy Academy) for technical support of computing platform on this research project. Ming Zhu was supported by National Natural Science Foundations of China (Grant No. 61902387). Christina Dan Wang is supported in part by National Natural Science Foundation of China (NNSFC) grant 11901395 and Shanghai Pujiang Program, China 19PJ1408200.

\newpage

\medskip
\small
\bibliographystyle{plain}
\bibliography{ref}

\input{NeurIPS_2020_version/appendix}


\end{document}




