So far, we have shown that VD is a powerful model with outstanding capacities. However, VD still has noticeable limitations in some aspects, such as image-to-text, \etc. In this session, we would like to discuss the limitation of our work as well as future research directions for improvements.

\textbf{Limited Latent Space:} During our experiment, we noticed that VD's major weakness is text generation (\ie image-to-text, text-variation, I2T2I). We believe that such weakness can be largely improved if we expand the scope and capacity of the Optimus VAE~\cite{optimus}. Unlike the AutoKL~\cite{ldm} (\ie the image VAE), which transforms images into latent features with dimension $4\times 64\times 64$, and thus keeps the necessary spatial information, Optimus's latent vectors are 768 single dimension vectors generated using Bert~\cite{bert} which may be inadequate for long text sentences. We believe that a better solution should adapt word locations and orders, forming a latent space of sequences, which makes text generation and restoration in later stages easier. In our experiment, we also noticed that VD tended to generate sentences with repeated descriptions, which partially proves our guess that the corresponding VAE is weak in understanding word locations and orders. 

\textbf{Imperfect Data:} Another issue that limited VD's performance was the imperfect text data we used in training. As mentioned in the main article Session 4.1, we formalized web-scraped prompts and captions with extensive engineering effort. We notice that with these cleaned captions, VD's training procedure on text-generation tasks had become more robust and easier to converge. Therefore, an immediate future target for VD research is to prepare a finetuned dataset that helps VD improve its model accuracy. Meanwhile, the pretrained Optimus VAE also had certain data limits. In our experiment, we noticed that Optimus VAE had difficulty reconstructing Laion2B captions. An example is shown below: "\textit{Assorted Cuff Colors Sandals Platform Leather Unique Ladies 1TO9 Cow Camel Ankle Brown EqBF6TT0}" (Laion2B), "\textit{leatherback canvas females posses exotic fruits terme white grass patchions}" (Optimus Reconstruction). We think the issue comes from a domain shift from Optimus's training data (\ie PTB~\cite{dataset_ptb}, SNLI~\cite{dataset_snli}, Yahoo and Yelp corpora~\cite{dataset_yahoo,dataset_yelp}) to VD's training data (\ie Laion2B~\cite{laion}), in which the former contains normal sentences with good grammar, and the latter contains long and descriptive sentences with online freestyle. Therefore, preparing a finetuned text VAE could be the critical next step for future VD research.