%\documentclass[letterpaper,twocolumn,10pt]{article}
\documentclass{article}             
\input{preamble}

%%% -------------------------------------------------------------------------

\title{Going in Style: Audio Backdoors through Stylistic Transformations}
 
\name{anonymous submission}
\address{}
\name{Stefanos Koffas$^{1,*}$, Luca Pajola$^{2,*}$, Stjepan Picek$^{3,1}$, Mauro Conti$^{2,1}$}    
 %TODO: Should we add our email addresses here?
 \address{$^1$Cybersecurity Group, Delft University of Technology, The Netherlands\\
          $^2$Security and Privacy Research Group, University of Padua, Italy\\
          $^3$Digital Security Group, Radboud University, The Netherlands\\
          $^*$Equal contribution}
\begin{document}
\maketitle

\begin{abstract}
A backdoor attack places triggers in victims' deep learning models to enable a targeted misclassification at testing time. 
In general, triggers are fixed artifacts attached to samples, making backdoor attacks easy to spot.
Only recently, a new trigger generation harder to detect has been proposed: the \textit{stylistic} triggers that apply stylistic transformations to the input samples (e.g., a specific writing style).
\par
Currently, stylistic backdoor literature lacks a proper formalization of the attack, which is established in this paper. 
Moreover, most studies of stylistic triggers focus on text and images, while there is no understanding of whether they can work in sound. This work fills this gap. 
We propose JingleBack, the first stylistic backdoor attack based on audio transformations such as chorus and gain.
% We examine audio effect transformations to demonstrate their feasibility in the sound domain.
Using 444 models in a speech classification task, we confirm the feasibility of stylistic triggers in audio, achieving 96\% attack success.


% \todo{complete when the paper is done}
% \todo{Mention that our code is public.}
\end{abstract}

\input{Sections/01-Introduction}
\input{Sections/02-Background}
\input{Sections/03-threat_model}
\input{Sections/06_case_study_speech_classification}
\input{Sections/08-Conclusions}

% Usenix
%\bibliographystyle{plain}
% ICASSP
% \bibliographystyle{IEEEbib}
\bibliographystyle{ieeetr}
\bibliography{sample}

\end{document}
