% for ICLR submit
\if\submission\submissionFinal
    \vspace{-0.5em}
    \section{Conclusion}
    \label{sec:conclusion}
    \vspace{-0.25em}
    This paper introduces a new modern ConvNet architecture, named MogaNet, through the lens of multi-order game-theoretic interaction.
    Built upon the modern ConvNet framework, we present a compact Moga Block and channel aggregation module to force the network to emphasize the expressive but inherently overlooked interactions across spatial and channel perspectives.
    Extensive experiments verify the consistent superiority of MogaNet in terms of both performance and efficiency compared to popular ConvNets, ViTs, and hybrid architectures on various vision benchmarks.
% 
\else
% for arXiv
% \if\submission\submissionarXiv
    \section{Conclusion}
    \label{sec:conclusion}
    In this paper, we introduce a new modern ConvNet architecture named MogaNet through the lens of multi-order game-theoretic interaction.
    % We demonstrate that using a spatial aggregation block and a channel aggregation block results in stronger feature interactions of intermediate complexities efficiently, boosting the performance of ConvNet architecture substantially on diverse vision scenarios.
    Built upon the modern ConvNet framework, we present a compact Moga Block and channel aggregation module to \pl{force the network to emphasize the expressive but inherently overlooked interactions} across spatial and channel spaces.
    %
    Extensive experiments demonstrate the consistent superiority of MogaNet in terms of both accuracy and computational efficiency compared to popular ConvNets, ViTs, and hybrid architectures on various vision benchmarks.
    We hope our work can prompt people to perceive the importance of multi-order interaction in representation learning and to facilitate the development of efficient deep architecture design.
%
\fi


\section*{Acknowledgement}
This work was supported by the National Key R\&D Program of China (No. 2022ZD0115100), the National Natural Science Foundation of China Project (No. U21A20427), and Project (No. WU2022A009) from the Center of Synthetic Biology and Integrated Bioengineering of Westlake University.
This work was done when Zedong Wang and Zhiyuan Chen interned at Westlake University. We thank the AI Station of Westlake University for the support of GPUs. We also thank Mengzhao Chen, Zhangyang Gao, Jianzhu Guo, Fang Wu, and all anonymous reviewers for polishing the writing of the manuscript.
