\section*{A: Appendix}  
\subsection*{Survey Form for User Study}
Zero-click spyware exploits zero-day (unknown) vulnerabilities in chat applications to stealthily compromise a smartphone without any user interaction.

Our solution curtails the risk of zero-click attacks by running chat apps in isolation at a remote instance, and allows the user to access chat apps via a screen sharing and remote control utility. In this way, if the attacker compromises one chat app, the targeted device and other chat apps remain unaffected. 

You can access the server by visiting https://34.xxx.xxx.xxx from your web browser. You are requested to use the system and provide your valuable feedback. We appreciate your time, effort and willingness to take part in this survey. 

\subsection*{A.1   Background Knowledge}
Have you had any idea about zero-click attacks prior to starting this user study?
\begin{itemize}
    \item Yes,
    \item No.
\end{itemize}

\subsection*{A.2   Remote Connection}
When connecting to the remote server, was the server accessible (in the first attempt) and the connection stable (i.e., it did not terminate after some time)?
\begin{itemize}
    \item Accessible and stable - I seamlessly connected to the remote end,
    \item Accessible but unstable - I connected for a while but the connection terminated later on,
    \item Inaccessible - I could not connect at all.
\end{itemize}

\subsection*{A.3  System's Usability}
Considering the need of a secure solution, do you find the system usable? 
\begin{itemize}
    \item Usable: user-friendly, text is readable, lag is acceptable (considering the immediate need of the solution and its benefits),
    \item Partially usable: user-friendly, text is readable, but experienced excessive lag,
    \item Not usable: Not user-friendly, text is not readable, and experienced excessive lag.
\end{itemize}

\subsection*{A.4  Suggestions}
What can we do to improve your experience (i.e., with regard to the system's performance and usability)?