\section{Background and State-Of-The-Art} \label{background-motivation}
\subsection{Zero-click Exploits}

Zero-click exploits tend to leverage common instant messaging applications such as WhatsApp and iMessage that, by design, receive messages and calls from anyone who knows the user's phone number, including untrusted sources.  
The attacker gears a zero-click attack by sending a specially-crafted hidden text message, image, or voicemail to the target device via a wireless connection (Wi-Fi, cellular network, Bluetooth, or NFC).  
The injected malicious code then provokes a previously unknown security vulnerability in an installed application to gain root access to the target device.    

Zero-click exploits are not new.  Apple first discovered a zero-click vulnerability on the iPhone 5 with iOS 6 in 2012~\cite{apple2012}.  
With the increase in attack sophistication and complex computing technologies, zero-click attacks have become a pervasive threat to smartphone users. 
Samsung recently patched a zero-click vulnerability in Skia (Android's graphics library) that existed in all Samsung smartphones sold since 2014~\cite{androidmms}.
Zero-click attacks have gained significant attention since the recent discovery of Pegasus, the zero-click spyware used to surveil high-profile individuals and organizations around the world.

\subsubsection*{\textbf{Pegasus Spyware}} 
Pegasus is a highly sophisticated cyber-espionage spyware created by NSO Group Technologies Ltd, an Israeli cybersecurity company, with the claimed aim of tracking terrorist activities via untraceable commands~\cite{pegasus}.
However, several reports claim that nation-state actors have misused Pegasus spyware to track the activities of their opponents and critics. 

In 2016, Apple discovered three zero-click exploits in iOS that were used to infect and spy on targets for years~\cite{forensics}.
In 2017, Pegasus spyware abused a zero-day vulnerability in WhatsApp with a mere unanswered message or call that enabled the spyware to run as a background resource and compromise the target phone. 
The Pegasus variants identified in 2020 and 2021 used two zero-click iMessage exploits; Kismet and ForcedEntry.  
Although Kismet was successful only against iOS release 13.5.1, ForcedEntry was exploited in the wild and even bypassed the iOS BlastDoor utility, which was basically designed to prevent such spyware attacks.  
Surprisingly, the 2021's Pegasus variant utilized the same vulnerability chaining technique, \textit{Trident}, as the 2016's Pegasus variant, which was patched by Apple right after the attack, albeit ineffectively~\cite{lookout}.

A key trait of Pegasus (and, in general, zero-click spyware) is that it does not show erratic behaviour or leave indicators of compromise (IoC) such as slow performance or excessive battery drainage.  
The spyware primarily exists in the phone's temporary memory (RAM) and is intermittently removed.  
Even upon installation on the phone, the spyware does not leave any trace.  
This way, it effectively evades detection by anti-malware or endpoint security systems, thereby failing to inform the user about the potential privacy infringement and taking security
threats to the next level. 

\subsubsection*{\textbf{Other zero-click spyware:}} 
Zero-click exploits now have a thriving market.  
Reign, zero-click spyware developed by QuaDream, can also compromise iOS devices using an iMessage-based zero-day exploit~\cite{reign}.  
In addition, sources claim that the zero-click exploits developed by Paragon~\cite{paragon} and Cognyte~\cite{threemore} can reportedly target end-to-end encrypted messaging applications, particularly WhatsApp and Signal to compromise the smartphone.  

\input{relatedwork}