\documentclass[11pt]{article}
%
\usepackage[top=3cm,bottom=3cm,left=2.5cm,right=2.5cm]{geometry}
\usepackage[round]{natbib}
\renewcommand{\bibname}{References}
\renewcommand{\bibsection}{\subsubsection*{\bibname}}
\input{preamble}
%
\usepackage{etoc} %
\usepackage[noblocks]{authblk}
\usepackage{graphicx}
\usepackage{comment}
\usepackage{fancyhdr}
%
\input{abhin-macros}
\input{raaz-macros}
%


\let\svthefootnote\thefootnote
\newcommand\freefootnote[1]{%
	\let\thefootnote\relax%
	\footnotetext{#1}%
	\let\thefootnote\svthefootnote%
}

%
%
%
%
%
%
%
%
%

%
%
\title{On counterfactual inference with unobserved confounding\freefootnote{This work was supported, in part, by NSF under Grant No. DMS-2023528 as part of the Foundations of Data Science Institute (FODSI), the MIT-IBM Watson AI Lab under Agreement No. W1771646, MIT-IBM projects on Time Series and Causal Inference as well as project with DSO National Laboratory.}}

%
%
%
%
\author[1]{Abhin Shah}
\author[1,2]{Raaz Dwivedi}
\author[1]{Devavrat Shah}
\author[1]{Gregory W. Wornell}

\affil[1]{Massachusetts Institute of Technology}
\affil[2]{Harvard University}


\graphicspath{{../figures/},{figs/}}
\input{cref_setup}
\date{}
\begin{document}
%
%

\begin{center}

  {\bf{\LARGE{On counterfactual inference with unobserved confounding}}}

\vspace*{.2in}


{\large{
\begin{tabular}{cccc}
Abhin Shah$^1$ & Raaz Dwivedi$^{1, 2}$ & Devavrat Shah$^1$ & Gregory W. Wornell$^1$ 
\end{tabular}
\begin{tabular}{c}
  \tt{\{abhin, raaz, devavrat, gww\}@mit.edu}
\end{tabular}
}}

\vspace*{.2in}

\begin{tabular}{c}
$^1$MIT and $^2$Harvard University
\end{tabular}

%

\today

\end{center}
\vspace*{.2in}


\input{abstract}
\etocdepthtag.toc{mtchapter}
\etocsettagdepth{mtchapter}{subsection}
\etocsettagdepth{mtappendix}{none}
%
%
%
%

%


%
\input{introduction}
\input{related_work}
\input{problem_formulation}
\input{algorithm}
\input{main_results}
\input{application}
\input{proof_sketch}
\input{discussion}
\subsubsection*{Acknowledgments}
The authors thank Thomas Courtade, Yuzhou Gu, Anuran Makur, Wenlong Mou, Felix Otto, and Yury Polyanskiy for helpful pointers regarding Logarithmic Sobolev inequalities.  The authors thank Yuval Dagan and Anthimos Vardis Kandiros for helpful discussion about \cite{DaganDDA2021} and \cite{KandirosDDGD2021}. The authors also thank Martin Wainwright and Avi Feller for helpful comments. Lastly, the authors thank the anonymous reviewers of Workshop on Causality for Real-world Impact (NeurIPS 2022) for their comments and suggestions.

\subsubsection*{Funding}
This work was supported, in part, by NSF under Grant No. DMS-2023528 as part of the Foundations of Data Science Institute (FODSI), the MIT-IBM Watson AI Lab under Agreement No. W1771646, MIT-IBM projects on Time Series and Causal Inference as well as project with DSO National Laboratory.
\appendix 
%
%
%
%
%
%
%

%
\pagestyle{fancy}
\fancyhf{} %
\renewcommand{\headrulewidth}{0pt}
\lhead{}
\chead{}
\rhead{}
\lfoot{}
%
\cfoot{\vspace{\baselineskip}\hyperlink{toc}{\thepage}}
\rfoot{}

%
\etoctocstyle{1}{Appendix}
\etocdepthtag.toc{mtappendix}
\etocsettagdepth{mtchapter}{none}
\etocsettagdepth{mtappendix}{section}
\etocsettagdepth{mtappendix}{subsection}
%


%
\addtocontents{toc}{\protect\hypertarget{toc}{}}
{\small\tableofcontents}

\counterwithin{mylemma}{section}
\counterwithin{mydefinition}{section}
\counterwithin{myproposition}{section}
\counterwithin{mycorollary}{section}

\input{A.tex}
\input{B.tex}
\input{C.tex}
\input{D.tex}
\input{E.tex}
\input{F.tex}
\input{G.tex}
\input{H.tex}
\bibliographystyle{abbrvnat}
\bibliography{main}

\end{document}