\documentclass{article}

%\usepackage{corl_2022} % Use this for the initial submission.
\usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
%\usepackage[preprint]{corl_2022} % Uncomment for pre-prints (e.g., arxiv); This is like ``final'', but will remove the CORL footnote.

\title{Learning Riemannian Stable Dynamical Systems\\ via Diffeomorphisms}

% The \author macro works with any number of authors. There are two
% commands used to separate the names and addresses of multiple
% authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to
% break the lines. Using \AND forces a line break at that point. So,
% if LaTeX puts 3 of 4 authors names on the first line, and the last
% on the second line, try using \AND instead of \And before the third
% author name.

% NOTE: authors will be visible only in the camera-ready and preprint versions (i.e., when using the option 'final' or 'preprint'). 
% 	For the initial submission the authors will be anonymized.

\author{
     Jiechao Zhang\textsuperscript{\ensuremath{1,2}}
     \quad
     Hadi Beik-Mohammadi\textsuperscript{\ensuremath{1,2}}
     \quad
     Leonel Rozo\textsuperscript{\ensuremath{1}}
 	\\
 	\textsuperscript{\ensuremath{1}}Bosch Center for Artificial Intelligence. Renningen, Germany.
 	\\
 	\textsuperscript{\ensuremath{2}.} Karlsruhe Institute of Technology (KIT), Karlsruhe, Germany.
 	\\
 	\href{mailto:leonel.rozo@de.bosch.com}{\textrm{leonel.rozo@de.bosch.com}} 
 	\quad
 	\href{mailto:hadi.beik-mohammadi@de.bosch.com}{\textrm{hadi.beik-mohammadi@de.bosch.com}}
}

\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{amsthm}
\usepackage{siunitx}
\usepackage{adjustbox}
\usepackage{bm}  % assumes amsmath package installed
\usepackage{graphics} % for pdf, bitmapped graphics files
\usepackage{epsfig} % for postscript graphics files
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[font=small,labelfont=small]{caption}
\usepackage{color}
% \usepackage[table]{xcolor}
\usepackage[ruled, linesnumbered, vlined]{algorithm2e}
\usepackage{sidecap}
\usepackage{tabularx}
\usepackage{booktabs} % Added for the table
% \usepackage{tikz}
% \usepackage{pgfplots}

%\usetikzlibrary{arrows.meta}
\newtheorem{theorem}{Theorem}

\graphicspath{{Images/}}

% New commands
\newcommand{\etal}{\MakeLowercase{\textit{et al.}}}
\newcommand{\SphereManifold}{\mathcal{S}}
\newcommand{\RtimeS}{\mathbb{R}^3 \times \mathcal{S}^3}
\newcommand{\trsp}{\mathsf{T}} % Transpose
\newcommand{\euclideanspace}{\mathbb{R}}
\newcommand{\manifold}{\mathcal{M}}
\newcommand{\tangentspace}[1]{\mathcal{T}_{#1}\mathcal{M}}
\newcommand{\expmap}[2]{\text{Exp}_{#1}(#2)}  % Exponential map of #2 at #1
\newcommand{\logmap}[2]{\text{Log}_{#1}(#2)}  % Logarithmic map of #2 at #1
\newcommand{\prltrsp}[3]{\Gamma_{#1 \rightarrow #2}\big(#3\big)}  % Parallel transport of #3 from #1 to #2
\newcommand{\diffeomorphism}{\psi}
\newcommand{\proju}{\operatorname{proju}}
\newcommand{\innerprod}[3]{\langle #2, #3 \rangle_{#1}}  % Inner product of #2 and #3 at #1
\newcommand{\manifolddist}[2]{d_{\manifold}(#1, #2)}
\begin{document}
\maketitle

%===============================================================================

\begin{abstract}
Dexterous and autonomous robots should be capable of executing elaborated dynamical motions skillfully.
Learning techniques may be leveraged to build models of such dynamic skills.
To accomplish this, the learning model needs to encode a stable vector field that resembles the desired motion dynamics. 
This is challenging as the robot state does not evolve on a Euclidean space, and therefore the stability guarantees and vector field encoding need to account for the geometry arising from, for example, the orientation representation.
To tackle this problem, we propose learning Riemannian stable dynamical systems (RSDS) from demonstrations, allowing us to account for different geometric constraints resulting from the dynamical system state representation.
Our approach provides Lyapunov-stability guarantees on Riemannian manifolds that are enforced on the desired motion dynamics via diffeomorphisms built on neural manifold ODEs.
We show that our Riemannian approach makes it possible to learn stable dynamical systems displaying complicated vector fields on both illustrative examples and real-world manipulation tasks, where Euclidean approximations fail. 
\end{abstract}

% Two or three meaningful keywords should be added here
\keywords{Dynamical systems, Riemannian manifolds, Motion learning} 

%===============================================================================

\input{Sections/Introduction}
%===============================================================================

\input{Sections/Background}

%===============================================================================

\input{Sections/Approach}

%===============================================================================

\input{Sections/Experiments}

%===============================================================================

\input{Sections/Discussion}


%===============================================================================

\clearpage
% The acknowledgments are automatically included only in the final and preprint versions of the paper.
\acknowledgments{J. Zhang was supported by the Bosch Center for Artificial Intelligence (BCAI) as a master thesis student.} 

%===============================================================================

% no \bibliographystyle is required, since the corl style is automatically used.
\bibliography{References}  % .bib

\clearpage
\appendix
\input{Sections/Appendix}


\end{document}
