\documentclass[11pt,a4paper,reqno, oneside]{amsart}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amscd}
\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{comment}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{ amssymb }
\usepackage[top=2.5cm]{geometry}
\usepackage[all]{xy}
\usepackage{caption}
\usepackage[english]{babel}
\pagestyle{plain}
\usepackage{physics}

%format theorems
\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{conj}[thm]{Conjecture}
\newtheorem{thmx}{Theorem}
\renewcommand{\thethmx}{\Alph{thmx}}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{openquest}[thm]{Open question}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{propx}{Proposition}
\renewcommand{\thepropx}{\Alph{propx}}

\theoremstyle{definition}
\newtheorem{defi}[thm]{Definition}
\newtheorem{ass}[thm]{Assumption}
\newtheorem{rem}[thm]{Remark}
\newtheorem{ex}[thm]{Example}

%math commands
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}

\newcommand{\Ham}{\mathrm{Ham}}
\newcommand{\HF}{\mathrm{HF}}
\newcommand{\CF}{\mathrm{CF}}
\newcommand{\Homol}{\mathrm{H}}
\newcommand{\Homeo}{\mathrm{Homeo}}
\newcommand{\Diff}{\mathrm{Diff}}
\newcommand{\Iso}{\mathrm{Iso}}
\newcommand{\Symp}{\mathrm{Symp}}
\newcommand{\vol}{\mathrm{vol}}
\newcommand{\supp}{\mathrm{supp}}
\newcommand{\frag}{\mathrm{frag}}
\newcommand{\cl}{\mathrm{cl}}

\def\vorlesungA#1#2#3#4#5#6{\noindent
\rlap{#1}\hfill \hspace{9mm} #4 \hfill\llap{#2} \\
#3\par\vskip+\parskip\vspace{7mm}
\centerline{{\LARGE #5\;#6}}
\vspace*{2ex}
}

\title{Floer cohomology of Dehn twists \\
along real Lagrangian spheres}
\author{Patricia Dietzsch}
\address{Department of Mathematics\\
  ETH Zürich\\
  Rämistrasse 101, 8092 Zürich, Switzerland}
\email{patricia.dietzsch@math.ethz.ch}

\begin{document}
\maketitle
%%%%%%%%%%%%%%%%%%%% Abstract %%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  We study the Floer cohomology of the Dehn twist
  along a real Lagrangian sphere in a symplectic manifold
  endowed with an anti-symplectic involution.
  We prove that there exists a distinguished element in the Floer group
  that is a fixed point of the automorphism induced by the involution. Our methods of proof are based on Mak-Wu's cobordism and Floer-theoretic considerations.
\end{abstract}

\section{Introduction and Main Results}\label{sec:Intro}
\input{Chapter1/Intro}
\subsection{Examples.}\label{subsec:Iexamples}
\input{Chapter1/Iexamples}
\subsection{Outline of Proof of Theorem \ref{I:thm:main}}\label{subsec:Ioutline_of_proof}
\input{Chapter1/Ioutline_of_proof}
\subsection{Organisation of the Paper.}\label{subsec:Iorg}
\input{Chapter1/Iorg}

%\newpage
\section{Dehn twist and real Lefschetz fibrations.}\label{sec:REALlefschetz}
\input{Chapter1/REALintro}
\subsection{Dehn twist.}\label{subsec:REALDehntwist}
\input{Chapter1/REALDehntwist}
\subsection{The Dehn twist as a monodromy.}\label{subsec:REALmonodromy}
\input{Chapter1/REALmonodromy}
\subsection{Real Lefschetz fibrations.}\label{subsec:REALdef}
\input{Chapter1/REALdef.tex}
\subsection{Splitting of the monodromy into anti-symplectic involutions.}\label{subsec:REALsplitting}
\input{Chapter1/REALsplitting.tex}
\subsection{Examples in $2$ dimensions.}\label{subsec:REAL2Dexamples}
\input{Chapter1/REAL2Dexamples.tex}

\section{Floer cohomology}\label{sec:HF}
\input{Chapter1/HFintro}
\subsection{Setting.}\label{subsec:HFsetting}
\input{Chapter1/HFsetting.tex}
\subsection{Conjugation invariance.}\label{subsec:HFconjugation_invariance}
\input{Chapter1/HFconjugation_invariance.tex}
\subsection{Lagrangian Floer cohomology.}\label{subsec:HFlag}
\input{Chapter1/HFlag.tex}
\subsection{Floer cohomology as a special case of Lagrangian Floer cohomology.}\label{subsec:HFcompare}
\input{Chapter1/HFcompare.tex}

\section{Lagrangian cobordisms}\label{sec:LC}
\subsection{Definition of a Lagrangian cobordism.}\label{subsec:LCdefinition}
\input{Chapter1/LCdefinition.tex}
\subsection{Lagrangian cobordisms induce cone decompositions.}\label{subsec:LCconedecomposition}
\input{Chapter1/LCconedecomposition.tex}

\section{Mak-Wu cobordism}\label{sec:MW}
\input{Chapter1/MWintro}
\subsection{The graph of the Dehn twist.}\label{subsec:MWGraphDT}
\input{Chapter1/MWGraphDT}
\subsection{The cobordism.}\label{subsec:MWcob}
\input{Chapter1/MWcob}
\subsection{Floer theory.}\label{subsec:MWsequence}
\input{Chapter1/MWsequence}

\section{Symmetry of the Mak-Wu cobordism}\label{sec:INV}
\input{Chapter1/INVintro}
\subsection{Linear approximation of anti-symplectic involution.}\label{subsec:INVlinear}
\input{Chapter1/INVlinear.tex}
\subsection{The symmetry of the surgery part.}\label{subsec:INVinvariance_Mak_Wu}
\input{Chapter1/INVinvariance_Mak_Wu.tex}
\subsection{The symmetry of the suspension part.}\label{subsec:INVinvariance_suspension}
\input{Chapter1/INVinvariance_suspension.tex}

\section{Background on Floer cohomology}\label{sec:ADD}
\subsection{Floer cohomology for symplectomorphisms.}\label{subsec:AdddefHF}
\input{Chapter1/ADDdefHF.tex}
\subsection{Lagrangian Floer cohomology.}\label{subsec:ADDdeflagHF}
\input{Chapter1/ADDdeflagHF.tex}
\subsection{Proof of Proposition \ref{HFcompare:prop}.}\label{subsec:ADDcompare}
\input{Chapter1/ADDcompare.tex}

%\appendix

\section*{Appendix A. Algebraic background.}\label{appendix}
\input{Appendix.tex}

\section*{Acknowledgements}
This work is part of my doctoral studies at ETH under the supervision of Paul Biran. I would like to express my deep gratitude to Paul Biran for his guidance, many patient explanations and for sharing his insights with me. I'm grateful to Jonny Evans for our conversation about examples. I would also like to thank Alessio Pellegrini for reading this work and helping to improve the paper. 
The author was partially supported by the Swiss National Science Foundation (grant number 200021 204107).


%\section{Plan}
%\input{Chapter1/plan}


%%%%%%%%%%%%%%%%%%%%% References %%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{aomalpha}
\bibliography{main}

\end{document}

