% \documentclass[a4,center,fleqn]{NAR}
% \documentclass[acmsmall]{acmart}[12pt]
\documentclass[camera,hyphens]{jpaper}
\input{packages}
\input{commands}

% Enter dates of publication
% \copyrightyear{YYYY}
% \pubdate{DD MM YYYY}
% \pubyear{YYYY}
% \jvolume{xx}
% \jissue{xx}

% %\articlesubtype{This is the article type (optional)}
% \newcites{supp}{Supplementary References}
% \setlength{\skip\footins}{1.2pc plus 10pt minus 2pt}
% \setlength{\footnotesep}{2pc}

\begin{document}
\sloppy
\title{\ltitle}



\maketitle
% \def\thefootnote{*}\footnotetext{These authors contributed equally to this work.}\def\thefootnote{\arabic{footnote}}
\input{sections/0_abstract}
\section*{Keywords}
genomics sequencing, basecalling, hardware acceleration, machine learning, deep neural network
\input{sections/1_introduction}
\input{sections/results}
% \input{sections/motivation}
\input{sections/4_discussion}
\input{sections/conclusion}
\input{sections/3_evaluation}

% \input{sections/5_conclusion}

\section{Data Availability}
\label{sec:data_avail}
The read set used in this study was downloaded from \url{https://bridges.monash.edu/articles/dataset/Raw_fast5s/7676174}, while the reference set can be downloaded from  \url{https://bridges.monash.edu/articles/dataset/Reference_genomes/7676135}.  
\Copy{CC1/1}{\hgb{For the human genome, we download reads from \mbox{\url{https://labs.epi2me.io/gm24385_2020.11/}}, while the reference genome is available at \mbox{\url{https://github.com/marbl/HG002}}.}} All trained models and generated reads can be downloaded from \url{https://zenodo.org/record/7413316}.
We ensure unbiased, fair, and consistent evaluation by retraining all the basecallers using the official ONT dataset~\mbox{\cite{bonito}}.

\section{Code Availability}
\hgb{Source code with the instructions for reproducing the results is publicly available at: }\url{https://github.com/Xilinx/neuralArchitectureReshaping}.
%Source code with the instructions for reproducing the results is shared and can be downloaded using \url{https://figshare.com/s/98b1396a85155c3f8b52} during the review process and will be published on GitHub upon acceptance to help researchers develop future hardware-optimized basecallers. We provide installation scripts for both NVIDIA and AMD GPUs.
Scripts used to perform basecalling accuracy analysis are available at: \url{https://github.com/rrwick/Basecalling-comparison}.
 %We will make it publicly available upon publication.
%https://github.com/CMU-SAFARI/RUBICON.


\section{Acknowledgments}
\gsssss{We thank the SAFARI Research Group members for their valuable feedback and the stimulating intellectual \gssssss{and} scholarly environment they provide. SAFARI Research Group acknowledges the generous gifts of their industrial partners, including Google, Huawei, Intel, Microsoft, VMware, and Xilinx. This research was partially supported by the Semiconductor Research Corporation. SAFARI Research Group acknowledges support from the European Union’s Horizon programme for research and innovation under grant agreement No. 101047160, project BioPIM.}
 Special thanks to  Alessandro Pappalardo for his support with quantization-aware training. We appreciate valuable discussions with Giovanni Mariani.  Thanks to AMD for providing access to the HPC fund cluster~\cite{hpcfund}. %We thank the SAFARI Research Group members for valuable feedback and the stimulating intellectual environment they provide. 

\section{Author Contributions}
 G.S., M.A., K.D., and A.K.  conceived \framework. G.S. designed and implemented \framework. %G.S., C.F., and M.C. collected data.  
 G.S., C.F., and M.C. collected data and performed the evaluations.  K.D., H.C., and O.M. supervised the work. %K.D. and O.M. acquired funding and supervised the project.  
 G.S., M.A.,  K.D., and C.F. wrote the manuscript. %G.S. produced the figures. 
All authors reviewed and edited the manuscript. All authors analyzed the results. All authors read and approved the final manuscript.  

\section{Competing Interests} 
All authors declare no competing interests.

% \section{Funding}
% O.M. and SAFARI Research Group are supported by funding from Intel, VMware, Semiconductor Research Corporation, the National Institutes of Health (NIH), and the ETH Future Computing Laboratory.
% % }


\newpage
\balance
% \bibliographystyle{IEEEtranS}
\bibliographystyle{vancouver}

{\small \bibliography{ref}}

\input{sections/supp}
% \input{revision}
\end{document}
